Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-14 latex/comp_or.tex
Queue give up worked fine

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims1data20.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims2data20.csv};

@@

	\end{center}
	\caption{ {\it mpShims} performance with $1.2 \times volume$. }
	\label{fig:mpShims2data20}
\end{figure}

Observing Figure \ref{fig:mpShims2data20}, it may be noticed that the best number of processes for {\it Scenario 1} (closest to the upper left corner) is \textbf{1}. For {\it Scenario 2}, the best number is \textbf{4}.

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims1data50.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims2data50.csv};

@@

	\end{center}
	\caption{{\it mpShims} performance with $1.5 \times volume$.}
	\label{fig:mpShims2data50}
\end{figure}

Observing Figure \ref{fig:mpShims2data50}, it may be noticed that the best number of processes for {\it Scenario 1} is \textbf{1}. For {\it Scenario 2}, the best number is \textbf{8}.

@@

	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpACO1data20.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpACO2data20.csv};

@@

	\end{center}
	\caption{{\it mpACO} performance with $1.2 \times volume$.}
	\label{fig:mpACO2data20}
\end{figure}

Observing Figure \ref{fig:mpACO2data20}, it may be noticed that the best number of processes for {\it Scenario 1} is \textbf{40}. For {\it Scenario 2}, the best number is \textbf{1}.

@@

	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpACO1data50.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpACO2data50.csv};

@@

	\end{center}
	\caption{{\it mpACO} performance with $1.5 \times volume$.}
	\label{fig:mpACO2data50}
\end{figure}

Observing Figure \ref{fig:mpACO2data50}, it may be noticed that the best number of processes for {\it Scenario 1} is \textbf{1}. For {\it Scenario 2}, the best number is \textbf{16}.

>>>>

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p1data20.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p2data20.csv};

@@

	\end{center}
	\caption{ {\it mpShims} performance with $1.2 \times volume$. }
	\label{fig:mpShimsdata20}
\end{figure}

Observing Figure \ref{fig:mpShimsdata20}, it may be noticed that the best number of processes for {\it Scenario 1} (closest to the upper left corner) is \textbf{1}. For {\it Scenario 2}, the best number is \textbf{4}.

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p1data50.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p2data50.csv};

@@

	\end{center}
	\caption{{\it mpShims} performance with $1.5 \times volume$.}
	\label{fig:mpShimsdata50}
\end{figure}

Observing Figure \ref{fig:mpShimsdata50}, it may be noticed that the best number of processes for {\it Scenario 1} is \textbf{1}. For {\it Scenario 2}, the best number is \textbf{8}.

@@

	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/ACO_p1data20.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/ACO_p2data20.csv};

@@

	\end{center}
	\caption{{\it mpACO} performance with $1.2 \times volume$.}
	\label{fig:mpACOdata20}
\end{figure}

Observing Figure \ref{fig:mpACOdata20}, it may be noticed that the best number of processes for {\it Scenario 1} is \textbf{40}. For {\it Scenario 2}, the best number is \textbf{1}.

@@

	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/ACO_p1data50.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/ACO_p2data50.csv};

@@

	\end{center}
	\caption{{\it mpACO} performance with $1.5 \times volume$.}
	\label{fig:mpACOdata50}
\end{figure}

Observing Figure \ref{fig:mpACOdata50}, it may be noticed that the best number of processes for {\it Scenario 1} is \textbf{1}. For {\it Scenario 2}, the best number is \textbf{16}.
